### 2017-01-01 paper/evaluation.tex
created macro for th # of stable subjects

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 25 were unable to fetch
all dependencies (\eg, due to the usage of a private library), and 128
were in an unstable revision. Our final set consists in 416 subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the 416 subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
to test each subject. The main loop (line 12) iterates over the list
of subjects and invokes the wrapper function \emph{run} to execute
Maven in separated steps (lines 14-16). To avoid inflating the
measured time, we first fetch all dependencies (line 14), compile the
source and test files (line 15) and later, we invoke Maven in offline
mode (line 16) to avoid package updates. In addition we randomly
selected 100 Maven logs to inspect and identify non-related tasks
(\eg, \emph{javadoc} generation and static analysis). We created a
list of plugins (lines 1-5) to ignore them during the test execution.
After the test execution, we use a simple regular expression over
the builder output to extract the elapsed time.

>>>>

\newcommand{\SubjCnt}{412}

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 26 were unable to
fetch all dependencies (\eg, due to the usage of a private library),
and 131 were in an unstable revision. Our final set consists in
\SubjCnt{} subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
to test each subject. The main loop (line 12) iterates over the list
of subjects and invokes the wrapper function \emph{run} to execute
Maven in separated steps (lines 14-16). To avoid inflating the
measured time, we first fetch all dependencies (line 14), compile the
source and test files (line 15) and later, we invoke Maven in offline
mode (line 16) to avoid package updates. In addition we randomly
selected 100 Maven logs to inspect and identify non-related tasks
(\eg, \emph{javadoc} generation and static analysis). We created a
list of plugins (lines 1-5) to ignore them during the test execution.
After the test execution, we use a simple regular expression over the
builder output to extract the elapsed time.
